### 2020-10-20 thesis/chap_1.tex
address comment 10

There are a number of ways to evaluate model performance in the context of land use change predictions. We used three different approaches:
\begin{itemize}
\item We report the $R^{2}$ resulting from the random forest model, as well as variable importance (evaluated as gini impurity score).
\item We used a ROC curve with Area Under the Curve (AUC) to compare true observed change with the predicted probabilities of transition. This method is often used in landscape ecology and land use change modeling \citep{pontius_recommendations_2014}.
\item We used a Conventional Cross Validation (CCV) method for the reporting of AUC values, with 10 folds, for which we also produce a measure of AUC with ROC curves.\\
\end{itemize}

>>>>

There are a number of ways to evaluate model performance in the context of land use change predictions. We used three different approaches:
\begin{itemize}
\item We report the goodness of fit ($R^{2}$ between data and prediction) of the random forest model, as well as variable importance (evaluated as gini impurity score).
\item We used a ROC curve with Area Under the Curve (AUC) to compare true observed change with the predicted probabilities of transition. This method is often used in landscape ecology and land use change modeling \citep{pontius_recommendations_2014}.
\item We used a Conventional Cross Validation (CCV) method for the reporting of AUC values, with 10 folds, for which we also produce a measure of AUC with ROC curves.\\
\end{itemize}
